\input{preamble}

\begin{document}

% +----------------------------------------------------------------------------+
% |                                P A G E   I                                 |
% +----------------------------------------------------------------------------+

\input{header.tex}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

\begin{fullwidth}
  Technophobic computer scientist, climber, dancer, psychology and philosophy
  interested and board game playing hippie. My PhD research is at the intersection
  between the areas of \emph{formal methods}, \emph{algorithms}, and
  \emph{complexity theory}.
\end{fullwidth}


% ----------------------------------------
% Side bar
% ----------------------------------------
\marginpar{
  % --------------------------------------
  % Education
  % --------------------------------------
  \cvsection{Education}

  \input{education/au_bsc.tex}

  \divider

  \input{education/au_msc.tex}

  % --------------------------------------
  % Skills
  % --------------------------------------
  \cvsection{Skills}

  Interpersonal Skills

  \input{skills/interpersonal.tex}

  \divider \\ Technologies

  \input{skills/technologies.tex}

  \divider \\ Theoretical Computer Science

  \input{skills/computer_science.tex}

  \divider \\ Mathematics

  \input{skills/mathematics.tex}
}

% ----------------------------------------
% Main page
% ----------------------------------------
\cvsection{Professional Experience}

\cvsubsection{Academic Experience}

\input{experience/phd.tex}

\cvsubsection{Industrial Experience}

\input{experience/scalgo.tex}

\medskip

\input{experience/it_minds.tex}

% +----------------------------------------------------------------------------+
% |                                P A G E   II                                |
% +----------------------------------------------------------------------------+
\newpage

% ----------------------------------------
% Side bar
% ----------------------------------------
\marginpar{
  % --------------------------------------
  % Languages
  % --------------------------------------
  \cvsection{Languages}

  \input{languages/english.tex}

  \divider

  \input{languages/danish.tex}

  \divider

  \input{languages/german.tex}

  % --------------------------------------
  % References
  % --------------------------------------
  \cvsection{References}

  \input{references/van_de_pol.tex}

  \divider

  \input{references/arnsfelt.tex}
}

% ----------------------------------------
% Main page
% ----------------------------------------

\cvsection{Teaching}
\input{experience/teaching_assistant.tex}

\medskip

\input{experience/supervision.tex}



% +----------------------------------------------------------------------------+
% |                                P A G E   III                               |
% +----------------------------------------------------------------------------+

\newpage
\begin{fullwidth}
  % --------------------------------------
  % Publications
  % --------------------------------------
  \cvsection{Publications}
  In order of publication (newest to oldest).

  \divider

  \cvsubsection{Published}

  \begin{itemize}
  \normalsize

  \item Steffan Christ Sølvsten, Jaco van de Pol, Anna Blume Jakobsen, and Mathias Weller Berg Thomasen.

        {\bf ``Adiar: Binary Decision Diagrams in External Memory''}.

        In: \emph{Tools and Algorithms for the Construction and Analysis of
        Systems}. Lecture Notes in Computer Science (LNCS), Vol. 13244. 2022,
        pp. 295--313.
        DOI: \doi{10.1007/978-3-030-99527-0\_16}.

        \divider

  \item Kristoffer Arnsfelt Hansen and Steffan Christ Sølvsten.

        {\bf ``$\exists$R-Completeness of Stationary Nash Equilibria in Perfect
        Information Stochastic Games''}.

        In: \emph{45th International Symposium on Mathematical Foundations of
        Computer Science}. Leibniz International Proceedings in Informatics
        (LIPIcs), Vol. 170. 2020

  \end{itemize}

  \divider

  \cvsubsection{In Submission}

  \begin{itemize}
  \normalsize

  \item Steffan Christ Sølvsten and Jaco van de Pol.

        {\bf ``Predicting Memory Demands of BDD Operations using Maximum Graph
        Cuts''}.

        In: \emph{Tools and Algorithms for the Construction and Analysis of
        Systems}. Lecture Notes in Computer Science (LNCS). 2023.

        \divider

  \item Steffan Christ Sølvsten and Jaco van de Pol.

        {\bf ``Adiar: Zero-suppressed Decision Diagrams in External Memory''}.

        In: \emph{International Symposium on Formal Methods}. Lecture Notes in
        Computer Science (LNCS). 2023.

  \end{itemize}

  % \nocite{*}    % HACK: Cite everything in the bibliography, so Biber fetches
  % \vspace{-2em} % HACK: Hide the space for 'Reference' section title

  % \printbibliography
\end{fullwidth}

% +----------------------------------------------------------------------------+
% |                         H E R E  B E  D R A G O N S                        |
% +----------------------------------------------------------------------------+
\iffalse
\cvsection{Volunteering}
I have been very active at the university outside of the studies. Below are some
things I have volunteered for among other things

\medskip

\input{volunteering/regnecentralen.tex}

\divider

\input{volunteering/tutor.tex}

\divider

\input{volunteering/fredagscafeen.tex}
\fi


\end{document}
